\documentclass[preprint,10pt]{article}
\date{}
\begin{document}

\noindent \textbf{Zhenbang Li} received the B.S. degree in computer science and technology from Beijing Institute of Technology, Beijing, China, in 2016. Currently, he is a Ph.D. student in Institute of Automation, Chinese Academy of Sciences, Beijing, China. His research interests include object tracking and deep learning.
\vspace{6mm}

\noindent \textbf{Qiang Wang} received the B.S. degree from University of Science and Technology Beijing, China in 2015. Currently, he is a Ph.D. student in Institute of Automation, Chinese Academy of Sciences, Beijing. His research interests include visual object tracking and target segmentation.
\vspace{6mm}

\noindent \textbf{Jin Gao} received the B.S. degree from the Beihang University, Beijing, China in 2010, and the Ph.D. degree from the University of Chinese Academy of Sciences (UCAS) in 2015. Now he is an assistant professor with the National Laboratory of Pattern Recognition, Institute of Automation, Chinese Academy of Sciences (CASIA). His research interests include visual tracking, autonomous vehicles, and service robots. 
\vspace{6mm}

\noindent \textbf{Bing Li} received the Ph.D. degree from the Department of Computer Science and Engineering, Beijing Jiaotong University, China, in 2009. He is currently an Associate Professor in the Institute of Automation, Chinese Academy of Sciences, Beijing, China. His research interests include video understanding, color constancy, visual saliency, and web content mining.
\vspace{6mm}

\noindent \textbf{Weiming Hu} received the PhD degree from the
Department of Computer Science and Engineering, Zhejiang University, in 1998. From April 1998
to March 2000, he was a postdoctoral research
fellow with the Institute of Computer Science and
Technology, Peking University. Now he is a
professor in the Institute of Automation, Chinese
Academy of Sciences. His research interests
include visual surveillance and filtering of Internet
objectionable information.
\vspace{6mm}

\noindent \textbf{Stephen J. Maybank} received the BA degree in mathematics from Kings College Cambridge in 1976, and the Ph.D. degree in computer science from Birkbeck College, University of London in 1988. He is currently a professor in the Department of Computer Science and Information Systems, Birkbeck College. His research interests include the geometry of multiple images, camera calibration, visual surveillance, etc. He is a fellow of the IEEE.
\vspace{6mm}
\end{document}

